%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-Source Contribution}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{General}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {robbyrussell/oh-my-zsh} % Role
    {OH-MY-ZSH -- Community-Driven Framework for Managing your ZSH Configuration.} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add Spotify CLI support.}
        \item {Improve MacOs features}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {sepandhaghighi/pycm} % Role
    {PYCM -- Multi-class Confusion Matrix Library in Python} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Fine-tune Models and fix bug.}
        \item {Add OSX Support.}
        \item {Add test and CI on Travis.}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {sepandhaghighi/qpage} % Role
    {QPAGE -- Free Project For Creating Academic Homepage Without Any Code In 3min} % Event
    {\textit{Co-Owner}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implementation of styles and templates.}
        \item {Add UNIX/MacOs Support.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {ECSIM/OPEM} % Role
    {OPEM -- Open Source PEM Fuel Cell Simulation Tool} % Event
    {\textit{Co-Owner}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {MacOs Support and maintenance.}
        \item {Implement Static Simulation Analysis.}
        \item {Implement Test and CI on Travis.}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {ECSIM/GOPEM} % Role
    {GOPEM -- GUI for OPEM Simulation} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in Python by \textbf{pyQt} and \textbf{matplotlib}}
        \item {Implement test and CI on Travis.}
        \item {Easy Install package deployed by \textbf{PyInstaller}.}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Mahi97/Spotify-AdBlocker} % Role
    {Spotify-AdBlocker -- Listen to Spotify - W/O Ads!} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written with \textbf{AppleScript}}
        \item {Mute, Replace and Remove ads from Spotify.}
      \end{cvitems}
    }

  \cventry
    {Mahi97/SpotifyControl} % Role
    {SpotifyControl -- Search and Play Music from Spotify in Terminal} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written with \textbf{AppleScript}}
        \item {Manage all Spotify functionality including search.}
      \end{cvitems}
    }

\end{cventries}

\cvsubsection{RoboCup \& FiraCup}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {RoboCup-SSL/grSim} % Role
    {GrSim -- RoboCup Small Size Robot Soccer Simulator } % Event
    {\textit{Maintainer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implement test and CI on Travis.}
        \item {Improve performance, fix bugs and add new rules and requirements.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {fira-simurosot/FIRASim} % Role
    {FIRASim -- FiraCup 2D Soccer Simulation Platform } % Event
    {\textit{Maintainer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implementation of Robot models.}
        \item {Add Win/Linux/OSX Support.}
        \item {Implement test and CI on Travis.}
        \item {Improve performance, fix bugs and add new rules and requirements.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {RoboCup-SimPlus/SimPlus-VRep} % Role
    {SimPlus -- The RoboCup Rescue Simulation environment for  Robocup Junior Rescue} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implementation of communication messages.}
        \item {Implementation of game server.}
        \item {Implementation of python client.}
        \item {Implementation of GRPC async protocol.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {RoboCup-SSL/ssl-vision} % Role
    {SSL-VISION -- Shared Vision System For The RoboCup Small Size League} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implementation of new rules and requirements.}
      \end{cvitems}
    }
    

    
    

    
\end{cventries}