%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-Source Contribution}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{General}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {robbyrussell/oh-my-zsh} % Role
    {OH-MY-ZSH -- Community-Driven Framework for Managing your ZSH Configuration.} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add Spotify CLI support to osx package.}
        \item {Improve MacOs features}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {sepandhaghighi/pycm} % Role
    {PYCM -- Multi-class Confusion Matrix Library in Python} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Fine-tune Models and fix bug.}
        \item {Add OSX Support.}
        \item {Add test and CI for OSX on travis.}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {sepandhaghighi/qpage} % Role
    {QPAGE -- Free Project For Creating Academic Homepage Without Any Code In 3min} % Event
    {\textit{Co-Owner}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implementation of styles and templates.}
        \item {Add UNIX/OSX Support.}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {ECSIM/OPEM} % Role
    {OPEM -- Open Source PEM Fuel Cell Simulation Tool} % Event
    {\textit{Co-Owner}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {OSX Support and maintenance.}
        \item {Implement Static Simulation Analysis.}
        \item {Implement Test and CI on Travis.}
      \end{cvitems}
    }
        \newline
%---------------------------------------------------------
  \cventry
    {ECSIM/GOPEM} % Role
    {GOPEM -- GUI for OPEM Simulation} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in Python by pyQt and matplotlib}
        \item {Implement test and CI on Travis.}
        \item {Easy Install package deployed by PyInstaller.}
      \end{cvitems}
    }

\end{cventries}

\cvsubsection{RoboCup}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {RoboCup-SSL/grSim} % Role
    {GRSIM -- RoboCup Small Size Robot Soccer Simulator } % Event
    {\textit{Maintainer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implement test and CI on Travis.}
        \item {Improve performance, fix bugs and add new rules and requirements.}
      \end{cvitems}
    }
        \newline

%---------------------------------------------------------
  \cventry
    {RoboCup-SSL/ssl-vision} % Role
    {SSL-VISION -- Shared Vision System For The RoboCup Small Size League} % Event
    {\textit{Contributer}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implementation of new rules and requirements.}
      \end{cvitems}
    }
\end{cventries}

\cvsubsection{Parsian Robotic Lab}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/ssl-visual-planner} % Role
    {ssl-visual-planner -- A User Friendly software to arrange plans for SSL league} % Event
    {\textit{Co-Owner}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implementation in \textbf{C++ and Qt}}
      \end{cvitems}
    }
        \newline

%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/ssl-fedit} % Role
    {SSL-FEDIT -- Formation Editor For SSL} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Migrated from RoboCup Soccer Simulation 2D}
        \item {Implemented in \textbf{C++ and Qt.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/Simurosot-Middle} % Role
    {Simurosot-Middle -- Simurosot Base Code MiroSot} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented in \textbf{C++ and VisualStudio.}}
        \item {Strong debug tools with network tools.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/Zero-Shot-Learning} % Role
    {ZeroShot Learning for ZJU AI Competition (GAN Approach)} % Event
    {\textit{Creator}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {GAN approach implementation}
        \item {Manifold implementation for classification}
      \end{cvitems}
    }

\end{cventries}

\cvsubsection{Mine}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Mahi97/Persian-Compiler} % Role
    {Persian-Compiler -- Just Another Persian Compiler} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in pure \textbf{C} with help of \textbf{Yacc} and \textbf{Flex}}
        \item {Support Recursive function, array and pointers}
      \end{cvitems}
    }
        \newline

    %---------------------------------------------------------
  \cventry
    {Mahi97/NUMEX-Lang} % Role
    {NUMEX-Lang -- The pure functional Interpreter for NUMEX Language} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{Racket} (a functional PL driven from Lisp)}
      \end{cvitems}
    }
        \newline

    %---------------------------------------------------------
  \cventry
    {Mahi97/Spotify-AdBlocker} % Role
    {Spotify-AdBlocker -- Listen to Spotify - W/O Ads!} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written with \textbf{AppleScript}}
        \item {Mute, Replace and Remove ads from Spotify.}
      \end{cvitems}
    }
    \newline
\cventry
    {Mahi97/OthelloPlayer} % Role
    {OthelloPlayer -- AI and Learning for Othello Game} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{Java}}
        \item {Implementation of Minimax Tree search with alpha-beta pruning and TD-Learning}
        \item {Genetic Learning script written in \textbf{Python} for tuning parameters}
      \end{cvitems}
    }
    %---------------------------------------------------------
% ParsianRoboticLab/RAIC2019
% ----
% C-Compiler
% SAYEH-Cache
% ----
% InvertSearch
% FSM
% ----
% MircroProject
% USART_GUI
% ----
% P2PFileTransfer
% Calc-Net
% ----
% MahiColabs
% ----
% Telegram
% SpotifyControl
% -----
% ClassicSearch
% Non-Classic-Search    


%---------------------------------------------------------
\end{cventries}

