\cvsection{Remarkable Projects}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/SSL-Visual-Planner} % Role
    {SSL Visual Planner -- A User Friendly software to arrange plans for SSL league} % Event
    {Parsian Robotic Lab.} % Location
    {Prof. Mohammad Azam Khosravi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Add OSX Support.}
        \item {Implementation in \textbf{C++ and Qt}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/ssl-fedit} % Role
    {SSL FEdit -- Formation Editor For SSL} % Event
    {Parsian Robotic Lab.} % Location
    {Prof. Mohammad Azam Khosravi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Migrated from RoboCup Soccer Simulation 2D}
        \item {Implemented in \textbf{C++ and Qt.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/RAIC2019} % Role
    {RAIC2019 -- RussianAICup, Soccer Platform using \textbf{Long Term Prediction}} % Event
    {Parsian Robotic Lab.} % Location
    {Prof. Mohammad Azam Khosravi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented in \textbf{Rust}}
        \item {Prediction of Ball and Agents in 3D Soccer Environment}
        \item {Multi-agent AI with Cooperation for Pass and Receive}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/Simurosot-Middle} % Role
    {Simurosot-Middle -- Simurosot Base Code MiroSot} % Event
    {Parsian Robotic Lab.} % Location
    {Prof. Mohammad Azam Khosravi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented in \textbf{C++ and VisualStudio.}}
        \item {Strong debug tools with network tools.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {ParsianRoboticLab/Zero-Shot-Learning} % Role
    {ZeroShot Learning for ZJU AI Competition (GAN Approach)} % Event
    {Parsian Robotic Lab.} % Location
    {Prof. Mohammad Azam Khosravi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {GAN approach implementation}
        \item {Manifold implementation for classification}
      \end{cvitems}
    }


   %---------------------------------------------------------
    \cventry
    {Mahi97/ClassicSearch} % Role
    {ClassicSearch -- Implementation of Classic Search Algorithms for some Classic Problems} % Event
    {Artificial Intelligence Course.} % Location
    {Prof. Ahmand Nikabadi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{C++}}
        \item {Implement Bidirectional, BFS, A*, DFS and UCS Searches.}
        \item {Model and Solve 2D Navigation, Puzzle 15 and Water Buckets Problems.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
    
    \cventry
    {Mahi97/Non-Classic-Search} % Role
    {Non-Classic-Search -- Beyond Search Algorithems} % Event
    {Artificial Intelligence Course.} % Location
    {Prof. Ahmand Nikabadi} % Date(s)
    {
      \begin{cvitems} % Description(s)
         \item {Written in \textbf{Python}}
        \item {Implement All sort of Hill Climbing, Genetic and Simulated Annealing}
        \item {Model and Solve 8 Queen, Math Equations and Graph Partitioning Problems.}
      \end{cvitems}
    }    
    %---------------------------------------------------------
    
    \cventry
    {Mahi97/OthelloPlayer} % Role
    {OthelloPlayer -- AI \& Learning for Othello Game} % Event
    {Artificial Intelligence Course.} % Location
    {Prof. Ahmand Nikabadi} % Date(s)
    {
      \begin{cvitems} % Description(s)
         \item {Written in \textbf{Java}}
        \item {Implement All MinMax Tree with \textbf{alpha-beta} pruning.}
        \item {Implementation of Opening Book and Ending Scenarios.}
        \item {Implementation of Genetic Optimizer to find weight through self-playing.}
      \end{cvitems}
    }
    %---------------------------------------------------------
    
    \cventry
    {Mahi97/InvertSearch} % Role
    {InvertSearch -- Positional Index and searching on Huge text data files with B-Trees} % Event
    {Data Structure Course.} % Location
    {Prof. Mahdi Dehghan Takhtefoladi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{C++ and Qt}}
        \item {All data structures like List and Vector implemented from Scratch.}
        \item {Using Balance trees for indexing and search.}
        \item {Multi-thread Processing.}
      \end{cvitems}
    }
    %---------------------------------------------------------
    
    \cventry
    {Mahi97/FSM} % Role
    {FSM -- Finite-State Machine, Automata, and Graph Computing} % Event
    {Data Structure Course.} % Location
    {Prof. Mahdi Dehghan Takhtefoladi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{C++ and Qt}}
        \item {Solve FSM language with backtracking.}
        \item {Remove Loop and improve the FSM.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mahi97/Persian-Compiler} % Role
    {Persian-Compiler -- Just Another Persian Compiler} % Event
    {Compiler Course.} % Location
    {Prof. Mohammad Reza Razzazi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in pure \textbf{C} with help of \textbf{Yacc} and \textbf{Flex}}
        \item {Support Recursive function, array and pointers}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Mahi97/NUMEX-Lang} % Role
    {NUMEX-Lang -- The Pure Functional Interpreter for Pure Functional Language} % Event
    {Programming Languages Course.} % Location
    {Prof. Mehran Soleyman Fallah} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{Racket} (a functional PL driven from Lisp)}
      \end{cvitems}
    }
    
    
    \cventry
    {Mahi97/LSTM\_FPGA} % Role
    {LSTM\_FPGA -- ~ Implementation of LSTM in FPGA with VHDL} % Event
    {FPGA Course.} % Location
    {Prof. Morteza Saheb Zamani} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{VHDL}}
        \item {Deployed of the \textbf{Xillinx Spartan 3} FPGA Hardware}
        \item {Train and Test for simple \textbf{Translation} from Greek to English}
      \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Mahi97/SAYEH} % Role
    {SAYEH -- Basic Computer (Simple Architecture Yet Enough Hardware!)} % Event
    {Computer Architecture Course.} % Location
    {Prof. Saeed Shiry Gheydari} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{VHDL}}
        \item {Implementation of \textbf{Memory} and \textbf{16-bit CPU} (ALU, Controller and Data Path)}
        \item {Implementation of \textbf{Pipeline} with \textbf{Branch Prediction}.}
        \item {Implementation of \textbf{Cache} with multiple strategy for SAYEH.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
    \cventry
    {Mahi97/C-Compiler} % Role
    {C-Compiler -- A Compiler to Generate SAYEH Assembly Instruction from C Source Code} % Event
    {Computer Architecture Course.} % Location
    {Prof. Saeed Shiry Gheydari} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{C++}}
        \item {Implementation of \textbf{Lexical} and \textbf{Syntax} Analysis}
        \item {Implementation of \textbf{Assembler}.}
      \end{cvitems}
    }
    
 

    %---------------------------------------------------------
    
    \cventry
    {Mahi97/USART\_GUI} % Role
    {USART\_GUI -- GUI Application that connect to any device for Read and Write via USART} % Event
    {Micro-Controller Course.} % Location
    {Prof. Mohammad Mahdi Homayounpour} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{C++ and Qt}}
        \item {Support every OS and Platform for execution}
        \item {Support all sort of device that use USART with any Frequency}
      \end{cvitems}
    }

    \cventry
    {Mahi97/MircroProject} % Role
    {MircroProject -- Receiving Morse Code from PC and Translate to Beep with any Frequency} % Event
    {Micro-Controller Course.} % Location
    {Prof. Mohammad Mahdi Homayounpour} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Design Electronic PCB with Altium Designer}
        \item {Assemble and Program the PCB}
        \item {Direct Connect to PC with USART}
      \end{cvitems}
    }
    %---------------------------------------------------------

    \cventry
    {Mahi97/P2PFileTransfer} % Role
    {P2PFileTransfer -- (Torrent) Sending File Peer-to-Peer over from multiple source and receiver} % Event
    {Network Course.} % Location
    {Prof. Masoud Sabaei} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{JAVA}}
        % \item {Support every OS and Platform for execution}
        \item {Distributed file transfer from multiple source to multiple destination}
      \end{cvitems}
    }

    %---------------------------------------------------------
    
    \cventry
    {Mahi97/CalcNet} % Role
    {CalcNet -- Distribute Calculation over Network} % Event
    {Network Course.} % Location
    {Prof. Masoud Sabaei} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written in \textbf{JAVA}}
        % \item {Support every OS and Platform for execution}
        \item {Use Master-Slave Architecture for task handling.}
      \end{cvitems}
    }
    %---------------------------------------------------------



%---------------------------------------------------------
\end{cventries}