%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Amirkabir University of Technology} % Job title
    {Artificial Intelligence Course - TA} % Organization
    {2 - Semester} % Location
    {Sep. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching Evolutionary Search and Optimization Algorithm}
        \item {Prepare the \textbf{Final Project} and \textbf{Grading} of home-works}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
\cventry
{Amirkabir University of Technology} % Job title
{Advance Programming Course - TA} % Organization
{1 - Semester} % Location
{Jan. 2018 - Jun. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Teaching \textbf{Bash}, \textbf{Git}, \textbf{Web Front-End} and \textbf{Databases} as side workshops}
    \item {Grade Home-works and review solutions in Class.}
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Amirkabir University of Technology} % Job title
{Basic Programming Course - TA} % Organization
{1 - Semester} % Location
{Sep. 2017 - Jan. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Teaching \textbf{C} and \textbf{C++}}
    \item {Review solutions of home-works in class}
  \end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Amirkabir University of Technology - Robotic Summer School} % Job title
    {Workshop Teacher} % Organization
    {4 - Summer} % Location
    {2015 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Being the Teacher of the event for four continuous year.}
        \item {Teaching \textbf{Linux}, \textbf{Git}, \textbf{C++}, \textbf{Python}, \textbf{Qt Frameworks}, \textbf{ROS Framwork} and \textbf{Gazebo} in Basic and Advance level in eighteen 6-hour sessions.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
    {Salam High School} % Job title
    {Robotic Teacher} % Organization
    {1 - Year} % Location
    {Sep. 2014 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teach embedded system programming on \textbf{Micro-Controllers} with C}
        \item {Teach basic algorithm, data structure and \textbf{C} Programming Language}
      \end{cvitems}
    }




\end{cventries}
